---
title: "Week 4 Project"
author: "Wen Che"
date: "September 1, 2017"
output: ioslides_presentation
---


## Brief Discription

We will use three datasets (cars/pressure/rock) from Rstudio.There are two parts for interactve:

* First, this app allows end user to choose dataset for visulaizing summary. 
* Second user can choose which dataset to get interactive plot.
     In the plot user can click and drag the selection box, 
     then linear regression line will generate based on chosen data. 

R code is too long to attach in the presentation. Just include main blocks.The more details are included in the additional link.


## ui.R
    
Allow the user to choose the datasets
```{r code1, eval=FALSE}
       selectInput(inputId = "option",label = "Choose a dataset:",
                   choices = c("rock", "pressure","cars")),
```
Allow the user to choose the plot to visualize linear regression 
```{r code2, eval=FALSE}
       radioButtons("plot_type","Select the plot to play with",
                    c("Visualize rock","Visualize pressure",...
```
Display the Slope for the user
```{r code3, eval=FALSE}
       h4("Slope from linear model"),
       textOutput("slopeOut"),
```
Display the plot and return rows which user choose to generate linear regression  
```{r code4, eval=FALSE}
    mainPanel(
      plotOutput("plot1",brush=brushOpts(
         id="brush1"))
```
## server.R
   Reactive function for dataset input, and another reaction function for Plot_type
```{r code5, eval=FALSE}
   optionInput <- reactive({switch(input$option,
                                   "rock" = rock,
                                   "pressure" = pressure,
                                   "cars" = cars)}
```
   Plot will be generated according to end user's input for "Select the plot to play with" 
```{r code6, eval=FALSE}
   output$plot1<-renderPlot({
    optionchoice<-optionInput()if(input$plot_type=="Visualize rock")
    {plot(rock$peri,...
```
## App Link
The project is developed by Shiny App from Rstudio.
The Shiny App is accessible from here:https://cloe64.shinyapps.io/speed_vs_stop_distance/


