---
title: "Week 4 Project"
author: "Wen Che"
date: "September 1, 2017"
output: ioslides_presentation
---


## Purpose 
This presentaion is about the final project for the Coursera Data Science Specialization Course: Developing Data Products.

We will use three datasets (cars/pressure/rock) from Rstudio.This app allows end user to chose the dataset and play with datasets plot to visualize the regression.
R code is too long to attach in the presentation. Just include main blocks.


## ui.R
    
    sidebarPanel(
       selectInput(inputId = "option",label = "Choose a dataset:",
                   choices = c("rock", "pressure","cars")),
       
       radioButtons("plot_type","Select the plot to play with",
                    c("Visualize rock","Visualize pressure","Visualize cars")),
       
       h4("Slope from linear model"),
       textOutput("slopeOut"),
       
       h4("Intercept from linear model"),
       textOutput("intOut")),
    
    mainPanel(
      plotOutput("plot1",brush=brushOpts(
         id="brush1"))

## server.R
   Reactive function for dataset input, and another reaction function will generate to choose the data points in the plot according to end user'        option for Plot_type
```{r code, eval=FALSE}
   optionInput <- reactive({switch(input$option,
                                   "rock" = rock,
                                   "pressure" = pressure,
                                   "cars" = cars)}
```
   Plot will be generated according to end user's choice for "Select the plot to play with" 
```{r code2, eval=FALSE}
   output$plot1<-renderPlot({
    optionchoice<-optionInput()if(input$plot_type=="Visualize rock")
    {plot(rock$peri,...
```
## App Link
The project is developed by Shiny App from Rstudio.
The Shiny App is accessible from here:https://cloe64.shinyapps.io/speed_vs_stop_distance/


